Proposed Solution

### 2016-01-29 intro1.tex
random

Fig.~\ref{fig-overview} describes an overview of our system. We start with
an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
follow the same naming conventions and we use that fact in a learning 
algorithm which will result with the rules describing the language model used in the files. Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them 
into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
language model. These rules are used for detecting errors violating the learned constraints in the files given by the user.

From a  practical perspective there is no additional burden 
to the users: they can use \app to verify their configuration files.

>>>>

Fig.~\ref{fig-overview} describes an overview of our system. We start with
an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
follow the same naming conventions and we use that fact in a learning 
algorithm which will result with the rules describing the language model used in the files. Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them 
into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
language model. The learning algorithm is template-based. We provide an initial set of
templates and the learner learns some concrete instances from 
the training set. For example, a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are integer variables. A rule that we might learn is that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$.
These rules are used for detecting errors violating the learned constraints in the files given by the user.

From a  practical perspective there is no additional burden 
to the users: they can use \app to verify their configuration files.
We support learning rules

present in the literature

modularity
